Sharing and organizing research products as R packages

### 2020-01-15 manuscript/manuscript.Rmd
Cut 5 words and fix typo.

A cornerstone of R are user-created packages, which contain functions, (meta)data, and documentation in a standard format that allows seamless sharing across users and operating systems. Data and functions in R packages are immediately available to others through the R console, and documentation can be viewed in R or online. We first outline how data and functions are included in R packages, and then turn to including other assets, such as manuscripts and posters. A complete guide to R packages is outside our scope; for a complete treatment, see Wickham [-@WickhamPackagesOrganizeTest2015].

@@

An additional benefit of the R package organizing principles is that the entire project can be easily showcased as a website (see Figure \@ref(fig:vertical-project-website). The website is compiled by *pkgdown* [@R-pkgdown] (click "Addins" -> "Build Vertical" in RStudio), which is automatically included with *vertical* projects. For instructions on customizing the website, see <https://pkgdown.r-lib.org/>.

>>>>

A cornerstone of R are user-created packages, which contain functions, (meta)data, and documentation in a standard format that allows seamless sharing across users and operating systems. Data and functions in R packages are immediately available to others through the R console, and documentation can be viewed in R or online. We first outline how data and functions are included in R packages, and then turn to including other assets, such as manuscripts and posters. A complete guide to R packages is outside our scope (see @WickhamPackagesOrganizeTest2015).

@@

An additional benefit of the R package organizing principles is that the entire project can be easily showcased as a website (see Figure \@ref(fig:vertical-project-website)). The website is compiled by *pkgdown* [@R-pkgdown] (click "Addins" -> "Build Vertical" in RStudio), which is automatically included with *vertical* projects. For instructions on customizing the website, see <https://pkgdown.r-lib.org/>.
